Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-28 ms.tex
comparison

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show a blackbody model (fit to the WFC3 data only).}
\label{fig:dayside}
\end{figure}

@@

\subsection{Comparison with GCMs}
\label{sec:gcm}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Planets}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, it is heated asymmetrically, its rotation rate is FIXME faster, and its surface gravity is lower.   To assess the effects of these comparative study with other objects of similar temperature, including field brown dwarfs and young directly imaged companions.

Sample of directly imaged planets

>>>>

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show the best fit blackbody (fit to the WFC3 data only).}
\label{fig:dayside}
\end{figure}

@@

\section{Comparison with GCMs}
\label{sec:gcm}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, the planet's other properties (surface gravity, rotation rate, irradiation) are different. To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.

We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature. Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).

The directly imaged spectra are taken from \cite{2008ApJ...689L.153L}, \cite{2010ApJ...719..497L}, \cite{2010A&A...512A..52B}, \cite{2011ApJ...729..139W} , \cite{2014A&A...562A.127B}, \cite{2011ApJ...730...42L}, \cite{2013ApJ...773...63A}, \cite{2016A&A...587A..56M}, \cite{2013ApJ...772...79A}, and \cite{2008ApJ...673L.185B}. They are calibrated\footnote{Apart for PZ Tel B whose flux calibration is detailed in \cite{2016A&A...587A..56M}.}in absolute flux using published H-band photometry \citep{2008ApJ...689L.153L, 2014A&A...562A.127B, 2011ApJ...729..139W, 2005A&A...430.1027C, 2011ApJ...730...42L, 2013ApJ...773...63A, 2003tmc..book.....C,2009A&A...506..799B} and distances \cite{2016A&A...595A...1G, 2007A&A...474..653V, 1999AJ....117..354D, 1999AJ....117.2381P}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

The main spectral feature over the wavelength range we consider is water. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (R_\mathrm{1.3} - R_\mathrm{1.5})/F_\mathrm{1.3}$, where $F_\mathrm{X}$ is the average flux in a wavelength bin $0.1\,\mu$m wide centered on a wavelength $X$, and $R_\mathrm{X}$ is the bin-averaged residual from the best fit blackbody. These intervals were chosen such that all of the data have complete spectral coverage over the bin.

%DI companions: 1RXSJ160929.1-210524b, J1610-1913B, TWA22A
%Age, logg, teff
%WASP-103b - logg = 3.2
